Transfer of Learned Opponent Models in Zero Sum Games

### 2021-09-16 Report/paper_draft_2021.Rmd
mixed effect models instead of anovas

#+ geom_boxplot(alpha=.4) + geom_point(position=position_jitterdodge(), alpha=.4) + ylab("Score") + xlab("Game") + facet_grid(. ~ condition) + theme_apa() + geom_hline(yintercept = 0, lty=2)

#geom_jitter(aes(colour=block, fill=block), width=.2) + facet_grid(. ~ condition)

# ggboxplot(x = "game", y = "block_score", colour="block", fill="block", add =c("mean_ci"), palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUMBERS"), ylab = "Score", xlab = "Game", legend.title = "Block") + geom_jitter(aes(color = block, fill = block), width = 0.2, alpha = 0.3 ) + facet_grid(. ~ condition)

```
On average, participants obtained the lowest score in the RPS game ($M = 0.289$, $SD = 0.348$), followed by Numbers ($M = 0.31$, $SD = 0.347$). Participants' performance was highest in the FWG game ($M = 0.454$, $SD = 0.354$). Scores in each game were significantly different from 0, the expected score of uniformly random play (RPS: $t(51) = 7.26$, $p < .001$;  FWG:  $t(51) = 10.04$ , $p < .001$; Numbers: $t(51) = 7.17$, $p < .001$). As uniformly random play is the Nash equilibrium, this indicates successful deviation from a Nash-optimal strategy.

To assess learning within and between games, we used a 2 (condition: Level 1, Level 2) by 3 (game: RPS, FWG, Numbers) by 2 (block: first half, second half) repeated-measures ANOVA, with the first factor varying between participants. This showed a main effect of Game ($F(2,100) = 8.54$, $\eta^{2}  = 0.05$,  $p < .001$), indicating that average scores varied significantly over the games. Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ($t(100) =3.78$, $p < .001$) and the Numbers game ($t(100) = 3.32$ , $p = .002$). The score in RPS was not significantly different from the score in Numbers ($t(100) = 0.45$ , $p = .65$). The main effect of Block ($F(1,50) = 22.51$ ,  $\eta^{2} = 0.03$, $p < .001$) shows that the score in the first half of each game ($M = 0.29$) was significantly lower than in the second half ($M = 0.40$), which indicates within-game learning. The main effect of Condition ($F(1,50) = 5.44$, $\eta^{2} = 0.05$, $p = .024$) indicates that scores were higher against the level-1 player ($M = 0.43$) than against the level-2 player ($M = 0.27$). Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.

@@

# Plot results by game and block (for all 3 games, learning is happening) 
dat2 %>%
  mutate(game = forcats::fct_recode(as.factor(game), RPS = "rps", FWG = "fwg", Numbers = "numbers")) %>%
  mutate(condition = factor(condition, levels = c("Level1", "Level2"))) %>%
  mutate(condition = forcats::fct_recode(condition, "Level 1" = "Level1", "Level 2" = "Level2")) %>%
  ggboxplot(x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","Numbers"), fill="block", ylab = "Percentage score", xlab = "Games") +  facet_grid(. ~ condition)

@@

tmp <- afex::aov_car(
  block_score ~ game.f*condition*block + Error(human_id/(game.f*block))
  , data=dat2
  , type = 3)

@@

@@

<!-- (ref:figure4-caption) Mean and standard error of early scores by game and opponent -->
```{r exp1-early-score-by-opp, fig.cap = "\\label{ref:figure4-caption}Performance in early rounds (2-6) per game and block across conditions in Experiment 1. Points are scores of individual participants and boxes reflect the 95\\% confidence intervals of the mean (center line equals the mean).", fig.align ='center', fig.width=8, fig.height=4}
exp1_dat2_6 %>%
  mutate(game = factor(game.f)) %>%
  mutate(game = forcats::fct_recode(game, Numbers = "Numbers")) %>%
  mutate(game = factor(game, levels = c("RPS", "FWG", "Numbers"))) %>%
  mutate(condition = factor(condition, levels = c("Level1", "Level2"))) %>%
  mutate(condition = forcats::fct_recode(condition, "Level 1" = "Level1", "Level 2" = "Level2")) %>%
  ggplot(aes(x = game, y = early_score, colour=game)) + stat_summary(fun.data = "mean_ci", geom = "crossbar")  + geom_jitter(alpha=.4) + ylab("Early score") + xlab("Game") + facet_grid(. ~ condition) + theme_apa() + geom_hline(yintercept = 0, lty=2) + scale_color_discrete() + theme(legend.position = "none")

#p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_se",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","Numbers"), ylab = "Early rounds score", xlab = "Games")

#p2 + facet_grid(. ~ condition)

@@

Next, we explore whether learning transfer is moderated by the type of opponent and game similarity. We expected better transfer between more similar games (i.e. better transfer from RPS to FWG than from RPS/FWG to Numbers), and worse transfer for the more sophisticated level-2 agent. Figure \ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 opponents. To explore this, we used a 2 (Condition: Level 1, Level 2) by 3 (Game: RPS, FWG, Numbers) repeated measures ANOVA with the first factor varying between participants. There was a main effect of Game ($F(1.84,91.77) = 3.35$, $\eta^{2}  = 0.04$,  $p = .043$, Greenhouse-Geisser correction applied to the degrees of freedom to correct for non-sphericity).

To test for transfer by type of opponent faced, we ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).  For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ($t(150) = 3.96$, $p < .001$) and Numbers ($t(150) = 3.74$, $p < .001$). For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ($t(150) = 2.48$, $p = .01$) but not to the dissimilar game of Numbers.

@@

To explore whether learning occurred within and between games, we performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) by two (Encounter: first or second) repeated-measures ANOVA, with the first factor varying between participants. This showed a main effect of Game ($F(1.85,88.7) = 11.81$, $\eta^{2} = 0.04$,  $p < .001$). Post-hoc pairwise comparisons between games ($p$-values adjusted using Holm method for multiple comparisons) indicate performance in the games increased steadily throughout the experiment, with FWG performance significantly higher than RPS ($t(96) =2.53$, $p = .025$), and performance in the Shootout game significantly higher than in FWG ($t(96) = 2.32$, $p = .025$). Whilst the ANOVA shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type ($F(1.7, 81.82) = 5.31$ ,$\eta^{2} = 0.02$,  $p = .01$). Follow-up analysis shows that when facing level-1 agents, scores increased steadily after each game, with FWG score significantly higher than RPS ($t(191) = 2.70$, $p = .03$) and Shootout scores in turn significantly higher than FWG  ($t(191) = 3.05$, $p = .01$). There was no significant difference between average scores on any two games when facing level-2 agents however.

@@

# plot scores per game 
#p2 <- ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_se",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Early rounds score", xlab = "Games", legend.title = "Games")

#p2 + facet_grid(. ~ opp_type)

@@

**To measure transfer between games, we again focus on participants’ scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}). We estimate a linear mixed effects model with the early round scores as the dependent variable, and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2) and Game (RPS, FWG, Shootout) as independent variables. Random model intercepts are assumed for participants. We found a main effect of Game($F(2,240) = 6.57$, $p = .002$) and an interaction effect between Game and Opponent type ( $F(2,240) = 3.34$,  $p = .037$).**

<!-- We performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) repeated-measures ANOVA, with the first factor varying between participants. This showed a main effect of Game ($F(1.94,92.98) = 7.67$, $\eta^{2} = 0.04$,  $p < .001$). **MS: Again, if there is no interaction, there might not be justification for running tests per opponent and game ** -->

We then ran statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer). For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ($t(271) = 4.99$, $p < .001$) and Shootout ($t(271) = 6.66$, $p < .001$). For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ($t(271) = 4.41$, $p < .001$). Unlike in Experiment 1, there is also evidence of transfer to the dissimilar Shootout game ($t(271) = 3.22$, $p = .004$).  The early round scores in the similar FWG games for level-1 and level-2 facing players are not significantly different from each other. However, the score of the players facing the level-1 opponent in Shootout is higher than that of players facing level-2 opponents ( $t(144) = 2.45$, $p = 0.01$).

@@

**The results of Experiment 2 confirm earlier results from Experiment 1 on learning transfer in a situation where participants need to learn about two distinct opponents. As in Experiment 1, participants adapted their strategies to both level-1 and level-2 opponents to exploit deviations from Nash-optimal play. Knowledge about both types of opponents were transferred to both the similar and dissimilar game. This transfer was moderated by the degree of similarity between games. The interaction effect showed that transfer to the dissimilar game was easier when facing the less sophisticated agent. **

@@

**$\phi_{t}$ can be interpreted as the discount on prior experiences, modelling either limited agent memory or changes in the game conditions. At the core, $\phi_{t}$ depends on the surprise index $ S_{p}(t)$**:

@@

**$S_{p}(t)$ quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play $ h_{k}(t)$**:

@@

**Where $I$ is the indicator function as defined above.  To get the surprise index, we simply sum all the squared deviations between the cumulative history vector $ h^{k}(t) $ and the immediate history $r^k(t)$**:

>>>>

```
First,we focus on participants scores oin each game (see Figure \ref{fig:exp1-avg-scores-game}). On average, participants obtained the lowest score in the RPS game ($M = 0.289$, $SD = 0.348$), followed by Numbers ($M = 0.31$, $SD = 0.347$). Participants' performance was highest in the FWG game ($M = 0.454$, $SD = 0.354$). Scores in each game were significantly different from 0, the expected score of uniformly random play (RPS: $t(51) = 7.26$, $p < .001$;  FWG:  $t(51) = 10.04$ , $p < .001$; Numbers: $t(51) = 7.17$, $p < .001$). As uniformly random play is the Nash equilibrium, this indicates successful deviation from a Nash-optimal strategy.

<!-- To assess learning within and between games, we used a 2 (condition: Level 1, Level 2) by 3 (game: RPS, FWG, Numbers) by 2 (block: first half, second half) repeated-measures ANOVA, with the first factor varying between participants. This showed a main effect of Game ($F(2,100) = 8.54$, $\eta^{2}  = 0.05$,  $p < .001$), indicating that average scores varied significantly over the games. Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ($t(100) =3.78$, $p < .001$) and the Numbers game ($t(100) = 3.32$ , $p = .002$). The score in RPS was not significantly different from the score in Numbers ($t(100) = 0.45$ , $p = .65$). The main effect of Block ($F(1,50) = 22.51$ ,  $\eta^{2} = 0.03$, $p < .001$) shows that the score in the first half of each game ($M = 0.29$) was significantly lower than in the second half ($M = 0.40$), which indicates within-game learning. The main effect of Condition ($F(1,50) = 5.44$, $\eta^{2} = 0.05$, $p = .024$) indicates that scores were higher against the level-1 player ($M = 0.43$) than against the level-2 player ($M = 0.27$). Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent. -->

**To assess learning within and between games, we estimate a linear mixed effects model with the scores as the dependent variable, and Condition (Level 1 or Level 2), Game (RPS, FWG, Numbers)  and Block ( first-half , second-half) as independent variables. Random model intercepts are assumed for participants.This showed a main effect of Game ($F(2,250) = 12.90$, $\eta^{2}  = 0.09$,  $p < .001$) indicating that average scores varied significantly over the games**. Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ($t(100) =3.78$, $p < .001$) and the Numbers game ($t(100) = 3.32$ , $p = .002$). The score in RPS was not significantly different from the score in Numbers ($t(100) = 0.45$ , $p = .65$). The main effect of Block ($F(2,250) = 15.16$ ,  $\eta^{2} = 0.06$, $p < .001$) shows that the score in the first half of each game ($M = 0.29$) was significantly lower than in the second half ($M = 0.40$), which indicates within-game learning. The main effect of Condition ($F(1,50) = 5.44$, $\eta^{2} = 0.10$, $p = .024$) indicates that scores were higher against the level-1 player ($M = 0.43$) than against the level-2 player ($M = 0.27$). Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent. **There was also an interaction effect of game by condition ($F(2,250) = 4.52$ ,  $\eta^{2} = 0.03$, $p = .01$)**

@@

# Plot results by game and block (for all 3 games, learning is happening) 
dat2 %>%
  mutate(game = forcats::fct_recode(as.factor(game), RPS = "rps", FWG = "fwg", Numbers = "numbers")) %>%
  mutate(condition = factor(condition, levels = c("Level1", "Level2"))) %>%
  mutate(condition = forcats::fct_recode(condition, "Level 1" = "Level1", "Level 2" = "Level2")) %>%
  ggboxplot(x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","Numbers"), fill="block", ylab = "Percentage score", xlab = "Games") +  facet_grid(. ~ condition)
```

@@

# tmp <- afex::aov_car(
#   block_score ~ game.f*condition*block + Error(human_id/(game.f*block))
#   , data=dat2
#   , type = 3)

mod1 <- mixed(block_score ~ game.f*condition*block + (1 | human_id),data=dat2,check_contrasts = FALSE, type = 3, method = "KR")
#summary(mod1)
mod1

# Get effect sizes from F values of mixed effect model
library(effectsize)
F_to_eta2(12.9, 2, 250)
F_to_eta2(5.44, 1, 50)
F_to_eta2(15.16, 1, 250)
F_to_eta2(4.52, 2, 250)

@@

library(afex)

# setting contrast to compare early score between games across levels 
contrasts(exp1_dat2_6$game.f) <- cbind(c(1,-1,0),c(0,-1,1))
contrasts(exp1_dat2_6$condition) <- c(1,-1)

# Mixed effects Model: Random intercept for participants
lme_early <- mixed(early_score ~ game.f*condition + (1 | human_id),data=exp1_dat2_6,check_contrasts = FALSE, type = 3, method = "KR")
summary(lme_early)

lme_early

@@

```{r exp1-early-score-by-opp, fig.cap = "\\label{ref:figure4-caption}Performance in early rounds (2-6) per game and block across conditions in Experiment 1. Points are scores of individual participants and boxes reflect the 95\\% confidence intervals of the mean (center line equals the mean).", fig.align ='center', fig.width=8, fig.height=4}

exp1_dat2_6 %>%
  mutate(game = factor(game.f)) %>%
  mutate(game = forcats::fct_recode(game, Numbers = "Numbers")) %>%
  mutate(game = factor(game, levels = c("RPS", "FWG", "Numbers"))) %>%
  mutate(condition = factor(condition, levels = c("Level1", "Level2"))) %>%
  mutate(condition = forcats::fct_recode(condition, "Level 1" = "Level1", "Level 2" = "Level2")) %>%
  ggplot(aes(x = game, y = early_score, colour=game)) + stat_summary(fun.data = "mean_ci", geom = "crossbar")  + geom_jitter(alpha=.4) + ylab("Early score") + xlab("Game") + facet_grid(. ~ condition) + theme_apa() + geom_hline(yintercept = 0, lty=2) + scale_color_discrete() + theme(legend.position = "none")

@@

Next, we explore whether learning transfer is moderated by the type of opponent and game similarity. We expected better transfer between more similar games (i.e. better transfer from RPS to FWG than from RPS/FWG to Numbers), and worse transfer for the more sophisticated level-2 agent. Figure \ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 opponents. We estimate a linear mixed effects model with the early round scores as the dependent variable, and Condition (Level 1 or Level 2) and Game (RPS, FWG, Numbers) as independent variables. Random model intercepts are assumed for participants. We found a main effect of Game ($F(2,100) = 3.35$, $p = .04$), and no main effect for condition. Further investigation of the effects of game on early score using planned contrasts revealed that early scores in the FWG games are significantly higher than in the RPS ( $t(99.99) = -2.32$, $p = 0.02$).

<!-- To explore this, we used a 2 (Condition: Level 1, Level 2) by 3 (Game: RPS, FWG, Numbers) repeated measures ANOVA with the first factor varying between participants. There was a main effect of Game ($F(1.84,91.77) = 3.35$, $\eta^{2}  = 0.04$,  $p = .043$, Greenhouse-Geisser correction applied to the degrees of freedom to correct for non-sphericity). -->

To delve deeper into the differences between participants learning transfer by opponent, we ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer). For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ($t(150) = 3.96$, $p < .001$) and Numbers ($t(150) = 3.74$, $p < .001$). For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ($t(150) = 2.48$, $p = .01$) but not to the dissimilar game of Numbers.

@@

xp2_anova <- afex::aov_car(
  int_score ~ (game.f*interaction_lvl*condition.f*opp_type) + Error(human_id/(game.f*interaction_lvl*opp_type))
  , data = dat_int
  , type = 3
)

mod2 <- mixed(int_score ~ game.f*interaction_lvl*condition.f*opp_type + (1 | human_id),data=dat_int,check_contrasts = FALSE, type = 3, method = "KR")
#summary(mod2)
mod2

F_to_eta2(15.32,2,528)
F_to_eta2(5.78,2,528)
```

<!-- To explore whether learning occurred within and between games, we performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) by two (Encounter: first or second) repeated-measures ANOVA, with the first factor varying between participants. This showed a main effect of Game ($F(1.85,88.7) = 11.81$, $\eta^{2} = 0.04$,  $p < .001$). Post-hoc pairwise comparisons between games ($p$-values adjusted using Holm method for multiple comparisons) indicate performance in the games increased steadily throughout the experiment, with FWG performance significantly higher than RPS ($t(96) =2.53$, $p = .025$), and performance in the Shootout game significantly higher than in FWG ($t(96) = 2.32$, $p = .025$). Whilst the ANOVA shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type ($F(1.7, 81.82) = 5.31$ ,$\eta^{2} = 0.02$,  $p = .01$). Follow-up analysis shows that when facing level-1 agents, scores increased steadily after each game, with FWG score significantly higher than RPS ($t(191) = 2.70$, $p = .03$) and Shootout scores in turn significantly higher than FWG  ($t(191) = 3.05$, $p = .01$). There was no significant difference between average scores on any two games when facing level-2 agents however. -->

**To explore whether learning occurred within and between game, we estimated a mixed effect model, with the participants scores as the dependent variable and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2), Game (RPS, FWG, Shootout) and Encounter (first or second) as the independent variables. Random model intercepts are assumed for participants. We found a main effect of Game ($F(2,528) = 15.32$, $\eta^{2} = 0.04$,  $p < .001$). Post-hoc pairwise comparisons between games ($p$-values adjusted using Holm method for multiple comparisons) indicate performance in the games increased steadily throughout the experiment, with FWG performance significantly higher than RPS ($t(96) =2.53$, $p = .025$), and performance in the Shootout game significantly higher than in FWG ($t(96) = 2.32$, $p = .025$). Whilst the mixed effect model shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type ($F(2, 528) = 5.78$ ,$\eta^{2} = 0.02$,  $p = .003$). Follow-up analysis differentiating performance by type of opponent faced shows that when facing level-1 agents, scores increased steadily after each game, with FWG score significantly higher than RPS ($t(191) = 2.70$, $p = .03$) and Shootout scores in turn significantly higher than FWG  ($t(191) = 3.05$, $p = .01$). There was no significant difference between average scores on any two games when facing level-2 agents however.**

@@

@@

**To measure transfer between games, we again focus on participants’ scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}). We estimate a linear mixed effects model with the early round scores as the dependent variable, and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2) and Game (RPS, FWG, Shootout) as independent variables. Random model intercepts are assumed for participants. We found a main effect of Game($F(2,240) = 6.57$, $p = .002$) and an interaction effect between Game and Opponent type ( $F(2,240) = 3.34$,  $p = .037$).**
```{r, include = FALSE}
# testing differences between early scores across games 
library(afex)

# Set contrasts
contrasts(exp2_dat2_6$game.f) <- cbind(c(1,-1,0),c(0,-1,1))
contrasts(exp2_dat2_6$opp_type) <- c(1,-1)
contrasts(exp2_dat2_6$condition.f) <- c(1,-1)

# Random intercecprt for participants
lme_early2 <- mixed(early_score ~ game.f*opp_type*condition.f + (1 | human_id),data=exp2_dat2_6,check_contrasts = FALSE, type = 3, method = "KR")
summary(lme_early2)

lme_early2
```
<!-- We performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) repeated-measures ANOVA, with the first factor varying between participants. This showed a main effect of Game ($F(1.94,92.98) = 7.67$, $\eta^{2} = 0.04$,  $p < .001$). **MS: Again, if there is no interaction, there might not be justification for running tests per opponent and game ** -->

We then ran statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer). For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ($t(271) = 4.99$, $p < .001$) and Shootout ($t(271) = 6.66$, $p < .001$). For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ($t(271) = 4.41$, $p < .001$). Unlike in Experiment 1, there is also evidence of transfer to the dissimilar Shootout game ($t(271) = 3.22$, $p = .004$).  The early round scores in the similar FWG games for level-1 and level-2 facing players are not significantly different from each other. However, the score of the players facing the level-1 opponent in Shootout is higher than that of players facing level-2 opponents ($t(144) = 2.45$, $p = 0.01$).

@@

**The results of Experiment 2 confirm earlier results from Experiment 1 on learning transfer in a situation where participants need to learn about two distinct opponents. As in Experiment 1, participants adapted their strategies to both level-1 and level-2 opponents to exploit deviations from Nash-optimal play. Knowledge about both types of opponents were transferred to both the similar and dissimilar game. This transfer was moderated by the degree of similarity between games. The interaction effect showed that transfer to the dissimilar game was easier when facing the less sophisticated agent.**

@@

**$\phi_{t}$ can be interpreted as the discount on prior experiences, modelling either limited agent memory or changes in the game conditions. At the core, $\phi_{t}$ depends on the surprise index $S_{p}(t)$ **:

@@

**$S_{p}(t)$ quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play $h_{k}(t)$**:

@@

**Where $I$ is the indicator function as defined above.  To get the surprise index, we simply sum all the squared deviations between the cumulative history vector $h^{k}(t)$ and the immediate history $r^k(t)$**:
